Reviewer comments from PeerJ

### 2015-03-06 PeerJ_trackchanges.tex
Comments and text, figures
Edits to locus figure. Weird box around it that we need to get rid of

%Figure 1 Locus Cartoon
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=180mm]{Fig1LocusCartoon.png}
   \flushleft{Figure 1. Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Region 1; within the 5' UTR, and Region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  \end{center}
\label{Fig1Cartoon}
\end{figure*}
%-------------------------------------------------------------------

>>>>

%Figure 1 Locus Cartoon
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=180mm]{Fig1Cartoon.png}
   \flushleft{Figure 1. Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Region 1; within the 5' UTR, and Region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion. The amplification product for the HopF/Hop R is either a 5kb band (an allele that includes the \emph{Hopscotch} insertion, or a 300bp band (an allele that does not include the \emph{Hopscotch} insertion. The HopF/HopIntR primer combination produces a 1.1kb band in individuals that have the \emph{Hopscotch} allele, and no band for individuals that lack the insertion, since the HopIntR primer sits within the LTR.}
  \end{center}
\label{Fig1Cartoon}
\end{figure*}
%-------------------------------------------------------------------
